My title

### 2024-02-12 paper/paper.qmd
slight readme update, added llm usage thus far, read fig 5 data

library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)

@@

fig_2d_data_long <- fig_2d_data %>%
  pivot_longer(cols = -year, names_to = "Education_Level", values_to = "Birth_Rate")
```

@@

# References

>>>>

library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(haven)

@@

fig_2d_data_long <- fig_2d_data %>%
  pivot_longer(cols = -year, names_to = "Education_Level", values_to = "Birth_Rate")

# acquire fig 5 data from nchs_cohort_analysis.dta
nchs_cohort_data <- 
  read_dta(here("data/nchs_cohort_analysis.dta"))
```

@@

```{r graph3, fig.cap="Children Ever Born by Mother’s Age and Birth Cohort", echo=FALSE}

#| label: fig-3

```
# References
